Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-08 loc1.tex
cleaned up the beginning bits a bit more.

  \newpage
  \section{Service Utilization and Performance}

@@

  One alternative to configuring the monitored endpoints from the user interface is to allow the service developer to annotate the code. This would however pollute the code, and prevent deploying two versions which would monitor different endpoints. Also, would pose problems with endpoint evolution in the future.

@@

    \item {\bf Utilization} -- refers to how the third parties use the API, which parts are most used, which are little used, etc. This is known to be critical information for upstream developers in general\cite{Haen14a}. In the case of source code dependencies one can detect such information by analyzing software repositories. However, in the case of services, there is no other way but monitoring service utilization.

>>>>

  \newpage
  \section{Service Utilization and Performance}
  \label{sec:utilandperf}

@@

  One alternative to configuring the monitored endpoints from the user interface is to allow the service developer to annotate the code. This would however pollute the code, and prevent deploying two versions which would monitor different endpoints. In addition, it would pose problems with endpoint evolution in the future.

@@

    \item {\bf Utilization} -- refers to how the third parties use the API, which parts are most used, which are less used, etc. This is known to be critical information for upstream developers in general\cite{Haen14a}. In the case of source code dependencies one can detect such information by analyzing software repositories. However, in the case of services, there is no other way but monitoring service utilization.

### 2018-04-08 outliers.tex

  When an API endpoint is called from within a highly interactive application 
    (as it is the case with \epTranslationsColor in the previous section) 
  of particular interest to the API developers are {\em performance outliers}.   
  Indeed, a translation request that takes three times more than expected can   decrease the perceived quality of the application. 
  Thus, identifying, collecting all appropriate data, and diagnosing the root   causes of such outliers is especially critical in improving the quality of an application.

>>>>

  When an API endpoint is called from within a highly interactive application 
    (as it is the case with \epTranslationsColor in the previous section) 
  of particular interest to the API developers are {\em performance outliers}.   
  Indeed, a translation request that takes three times more than expected can   decrease the perceived quality of the application significantly. 
  Thus, identifying, collecting all appropriate data, and diagnosing the root   causes of such outliers is especially critical in improving application quality.
